Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-25 manuscript/manuscript.Rmd
reward-> harvest in plot

p2 <- msy_tac_ppo |> 
    group_by(rep, policy) |>
    filter(t==max(t), species == "X", rep < 30) |>
    ggplot(aes(rep, reward)) + 
      geom_col() +
      facet_wrap(~factor(policy, levels = c("msy", "tac", "ppo")), labeller = policy_labeller ) +
      labs(y = "episode reward", x = "repetition") +
      theme(axis.text.x = element_blank())

>>>>

p2 <- msy_tac_ppo |> 
    group_by(rep, policy) |>
    filter(t==max(t), species == "X", rep < 30) |>
    ggplot(aes(rep, reward)) + 
      geom_col() +
      facet_wrap(~factor(policy, levels = c("msy", "tac", "ppo")), labeller = policy_labeller ) +
      labs(y = "episode harvest", x = "repetition") +
      theme(axis.text.x = element_blank())
